Parallelizing Linear Recurrent Neural Nets Over Sequence Length

### 2018-04-22 poster/main.tex
Added first pass at poster results with modified graph

\begin{block}{Mathematical Section}

Nam quis odio enim, in molestie libero. Vivamus cursus mi at nulla elementum sollicitudin. Nam quis odio enim, in molestie libero. Vivamus cursus mi at nulla elementum sollicitudin.

\begin{equation}
E = mc^{2}
\label{eqn:Einstein}
\end{equation}

Nam quis odio enim, in molestie libero. Vivamus cursus mi at nulla elementum sollicitudin. Nam quis odio enim, in molestie libero. Vivamus cursus mi at nulla elementum sollicitudin.

\begin{equation}
\cos^3 \theta =\frac{1}{4}\cos\theta+\frac{3}{4}\cos 3\theta
\label{eq:refname}
\end{equation}

Nam quis odio enim, in molestie libero. Vivamus cursus mi at nulla elementum sollicitudin. Nam quis odio enim, in molestie libero. Vivamus cursus mi at nulla elementum sollicitudin.

\begin{equation}
\kappa =\frac{\xi}{E_{\mathrm{max}}} %\mathbb{ZNR}
\end{equation}

@@

\begin{block}{Results}

\begin{figure}
\includegraphics[width=0.8\linewidth]{placeholder.jpg}
\caption{Figure caption}
\end{figure}

Nunc tempus venenatis facilisis. Curabitur suscipit consequat eros non porttitor. Sed a massa dolor, id ornare enim:

\begin{table}
\vspace{2ex}
\begin{tabular}{l l l}
\toprule
\textbf{Treatments} & \textbf{Response 1} & \textbf{Response 2}\\
\midrule
Treatment 1 & 0.0003262 & 0.562 \\
Treatment 2 & 0.0015681 & 0.910 \\
Treatment 3 & 0.0009271 & 0.296 \\
\bottomrule
\end{tabular}
\caption{Table caption}
\end{table}

>>>>

\begin{block}{Beating CuDNN: Synthetic Data}

  We tested the GILR-LSTM by comparing to the CuDNN LSTM implementation
  on a synthetic memorisation task (problem 2b from %\citet{hochreiter1997long}. )
  We compared the performance on variants with different values of
  \(n\).  We obtained speedups of over 6x measured in wall clock time to
  convergence.  Further, the GILR-LSTM attained convergence
  when the time dependence of the problem had a length of \textbf{one  million time steps}.

 \vspace{2em}
\begin{figure}
\includegraphics[width=1.0\linewidth]{8k_for_poster.png}
\caption{Accuracy on the memorisation task with 8,192 sequence length}
\end{figure}

@@

\begin{block}{Accelerating existing linear RNNs}
  We implemented several recent linear RNNs with the parallel linear
  recurrence kernel, as well as a variant with purely serial evaluation.
  We were able to obtain significant speedups with parallel evaluation
  in all the architectures at longer sequence lengths.

  Since the parallel kernel computes the exact same result as the
  serial kernel, we obtain this speedup with no tradeoff in terms of
  reduced accuracy or precision.

  [Can be cut if no space]
  We used two stacked RNN layers with 256 hidden
  units, keeping the GPU memory usage constant by fixing $bT = 65,536$
  for minibatch size $b$ and sequence length $T$. QRNN(2) refers to a
  QRNN with filter size 2. %\citep{bradbury2017quasi}

\begin{table}[t]
  \vspace{2ex}
  \caption{Parallel kernel speedup for a variety of LS-RNNs.}
\begin{center}
\begin{tabular}{lrrrr}
\label{table:rnn-throughput}
\small{Seq.\ Len.} & \small{SRU} & \small{QRNN(2)}
  & \small{QRNN(10)} & \small{GILR-LSTM}\\ \midrule
16 & 0.28 & 0.38 & 0.78 & 0.61\\
256 & 0.84 & 0.86 & 0.99 & 0.91\\
4,096 & 1.38 & 1.18 & 1.05 & 0.98\\
65,536 & 9.21 & 6.68 & 2.05 & 1.41\\ \bottomrule
\end{tabular}
\end{center}
\end{table}
\end{block}

% \begin{table}
% \vspace{2ex}
% \begin{tabular}{l l l}
% \toprule
% \textbf{Treatments} & \textbf{Response 1} & \textbf{Response 2}\\
% \midrule
% Treatment 1 & 0.0003262 & 0.562 \\
% Treatment 2 & 0.0015681 & 0.910 \\
% Treatment 3 & 0.0009271 & 0.296 \\
% \bottomrule
% \end{tabular}
% \caption{Table caption}
% \end{table}

% \end{block}
